FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-02 header.tex
add latexmkrc, rebuild header etc

\title{My JuliaCon proceeding}

@@

\keywords{Julia, Optimization, Game theory, Compiler}

\hypersetup{
pdftitle = {My JuliaCon proceeding},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {1st author, 2nd author, 3rd author},
pdfkeywords = {Julia, Optimization, Game theory, Compiler},
}

>>>>

\title{FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions}

@@

\keywords{Julia, Floating point, Numerical computing}

\hypersetup{
pdftitle = {FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Taylor Allred, Xinyi Li, Ashton Wiersdorf, Ben Greenman, Ganesh Gopalakrishnan},
pdfkeywords = {Julia, Floating point, Numerical computing},
}
